---
headcolor: 00785c
name: Florian
surname: W&uuml;nnemann
position: "Postdoctoral fellow at the Lettre lab"
address: "Montreal Heart Institute"
# phone: +1 514 516 6667
www: florianwuennemann.com
email: "flowuenne@gmail.com"
twitter: flowuenne
github: flowuenne
#linkedin: florian-w&uuml;nnemann-322357189
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "**Research and scientific interests**:	Human genetics, Single cell OMICS, Heart development, Bioinformatics, Interactive data visualizations"
docname: 
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
```

# Experience

```{r}
library(tibble)
tribble(
  ~ Title, ~ Year, ~ Institution, ~ Where, ~ Details,
  "Postdoc", "Aug. 2018- ongoing", "Montreal Heart Institute", "Montreal, Canada", "Single-cell technologies, Polygenic risk scores, Large-scale CRISPR applications, Atherosclerosis") %>% 
  detailed_entries(Title, Year, Institution, Where, Details)
```


# Education

```{r}
library(tibble)
tribble(
  ~ degree, ~ Year, ~ Institution, ~ Where, ~ Details,
  "Ph.D. (Dr.rer.nat)", "Apr. 2014 - Apr.2018", "University of Münster / CHU Sainte Justine Research Center", "Münster, Germany / Montreal, Canada", "The role of genetic factors in pathogenesis and progression of cardiac malformations",
  "MSc - Life sciences", "Oct. 2011 - Feb. 2014", "University of  Münster", "Münster, Germany", "Functional and genetic characterization of a novel arrhythmic syndrome",
  "BSc - Physiology", "Oct. 2008 - Sep. 2011", "University of  Münster", "Münster, Germany",  "Impact of nutrient limitation in insects: Comparative genomics of the pea aphid and the human body louse"
) %>%
  
  
  detailed_entries(degree, year, institution, where, details)
```

# Research Experience

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Institution, ~ Where, ~ Group,
  "Student Research assistant", "Jan. 2012 - Jul.2012", "IEB, University of  Münster", "Münster, Germany", "Acquisti group",
  "Student assistant", "Sep. 2011 - Dec. 2011", "IEB, University of  Münster", "Münster, Germany", "Acquisti group",
  "Student assistant", "Mar.2011 - May 2011", "IEB, University of  Münster", "Münster, Germany","Bornberg-Bauer group"
) %>% 
  detailed_entries(Position, Year, Institution,Where, Group)


readr::read_csv("presentations.csv") %>% 
  subset(type == "Oral") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title,
                   where = location)
```

# Funding

```{r}
readr::read_csv("scholarships.csv") %>% 
   brief_entries(what = scholarship, 
                 when = glue::glue("{start} - {end}"))
```


# Achievements and Awards

```{r}
readr::read_csv("awards.csv") %>% 
   brief_entries(what = award, when = year)
```


# Presentations

```{r presentations}
readr::read_csv("presentations.csv") %>% 
  subset(type == "Oral") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title,
                   where = location)
```

# Poster presentations

```{r}
readr::read_csv("presentations.csv") %>% 
  subset(type == "Poster") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title, where = location)
```

# Publications

```{r}
# library(dplyr)
# 
# bibliography_entries("references.bib") %>%
#   arrange(desc(issued))
```

- **Wünnemann, F.**, Tadjo, T. F., Beaudoin, M., Lalonde, S., Lo, K. S., & Lettre, G. (2021). CRISPR perturbations at many coronary artery disease loci impair vascular endothelial cell functions. bioRxiv.

- **Wünnemann, F.**&ast, Ta‐Shma, A.&ast, Preuss, C., Leclerc, S., Vliet, P. P. van, Oneglia, A., Thibeault, M., Nordquist, E., Lincoln, J., Scharfenberg, F., & others. (2020). Loss of ADAMTS19 causes progressive non‐syndromic heart valve disease. Nature Genetics, 52(1), 40–47.
**&ast;Authors contributed equally**

- Audain, E., Wilsdon, A., Breckpot, J., Izarzugaza, J. M., Fitzgerald, T. W., Kahlert, A., Sifrim, A., **Wuennemann, F.**, Perez‐Riverol, Y., Abdul‐Khaliq, H., & others. (2020). Integrative analysis of genomic variants reveals new associations of candidate haploinsufficient genes with congenital heart disease. bioRxiv.

- Gould, R. A., Aziz, H., Woods, C. E., Seman‐Senderos, M. A., Sparks, E., Preuss, C., **Wünnemann, F.**, Bedja, D., Moats, C. R., McClymont, S. A., & others. (2019). ROBO4 variants predispose individuals to bicuspid aortic valve and thoracic aortic aneurysm. Nature Genetics, 51(1), 42–50.

- Luyckx, I., Kumar, A. A., Reyniers, E., Dekeyser, E., Vanderstraeten, K., Vandeweyer, G., **Wünnemann, F.**, Preuss, C., Mazzella, J.‐M., Goudot, G., & others. (2019). Copy number variation analysis in bicuspid aor‐ tic valve‐related aortopathy identifies TBX20 as a contributing gene. European Journal of Human Genetics, 27(7), 1033–1043.

- **Wünnemann, F.**, Sin Lo, K., Langford‐Avelar, A., Busseuil, D., Dubé, M.‐P., Tardif, J.‐C., & Lettre, G. (2019). Validation of genome‐wide polygenic risk scores for coronary artery disease in french canadians. Circulation: Genomic and Precision Medicine, 12(6), e002481.

- Gillis, E., Kumar, A. A., Luyckx, I., Preuss, C., Cannaerts, E., Van De Beek, G., Wieschendorf, B., Alaerts, M., Bolar, N., Vandeweyer, G., & **others.** (2017). Candidate gene resequencing in a large bicuspid aortic valve‐ associated thoracic aortic aneurysm cohort: SMAD6 as an important contributor. Frontiers in Physiology, 8, 400.

- **Wünnemann, F.**, Kokta, V., Leclerc, S., Thibeault, M., McCuaig, C., Hatami, A., Stheneur, C., Grenier, J.‐C.,
Awadalla, P., Mitchell, G. A., & others. (2016). Aortic dilatation associated with a de novo mutation in the SOX18 gene: Expanding the clinical spectrum of hypotrichosis‐lymphedema‐telangiectasia syndrome. Canadian Journal of Cardiology, 32(1), 135–e1.

- Preuss, C.&ast, Capredon, M.&ast, **Wünnemann, F.**&ast, Chetaille, P., Prince, A., Godard, B., Leclerc, S., Sobreira, N., Ling, H., Awadalla, P., & others. (2016). Family based whole exome sequencing reveals the multifaceted role of notch signaling in congenital heart disease. PLoS Genetics, 12(10), e1006335.
**&ast;Authors contributed equally**

- Chetaille, P., Preuss, C., Burkhard, S., Côté, J.‐M., Houde, C., Castilloux, J., Piché, J., Gosset, N., Leclerc, S.,
**Wünnemann, F.**, & others. (2014). Mutations in SGOL1 cause a novel cohesinopathy affecting heart and gut rhythm. Nature Genetics, 46(11), 1245.

