---
headcolor: 00785c
name: Florian
surname: W&uuml;nnemann
position: "Postdoc in the Schapiro lab"
address: "Im Neuenheimer Feld 130, 69120 Heidelberg, Germany"
# phone: +1 514 516 6667
www: florianwuennemann.com
email: "flowuenne@gmail.com"
twitter: flowuenne
github: flowuenne
#linkedin: florian-w&uuml;nnemann-322357189
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "**Research and scientific interests**:	Human genetics, Single cell OMICS, Heart development, Bioinformatics, Machine Learning, Computer vision, Open source software"
docname: RÉSUMÉ
output: 
  vitae::awesomecv:
    keep_tex: false
always_allow_html: yes
header-includes:
  \usepackage{float}
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)
library(glue)
library(fontawesome)
library(here)
```

Research experience
============================

```{r, research_experience}
readr::read_csv(here("./data/experience.csv")) %>% 
  detailed_entries(what = position, 
                   when = glue::glue("{start} - {end}"),
                   with = institution,
                   where = where,
                   description)
```


Education
============================

```{r, education}
library(tibble)
readr::read_csv(here("./data/education.csv")) %>%
  detailed_entries(what = degree,
                   when = glue("{start} - {end}"),
                   with = institution,
                   where = where,
                   details)
```

Funding History
============================

```{r, funding}
readr::read_csv(here("./data/scholarships.csv")) %>% 
   detailed_entries(what = scholarship, 
                 when = glue::glue("{start} - {end}"))
```


Achievements and Awards
============================

```{r, awards}
tribble(~time, ~award, ~place,
        "2021/06","Poster prize: Prix Fonds de recherche du Québec (FRQS) (Recherche fondamentale doctorale / Postdoc)","Montreal,Canada",
        "2019/06","Best oral presentation award, 22nd Montreal Heart Institute research day","Montreal,Canada",
        "2017/05","Best oral presentation award, 32nd student congress at the CHU Sainte-Justine","Montreal, Canada",
        "2016/05","Markwald award for best oral presentation, Weinstein Cardiovascular Development and Regeneration Conference 2016","Durham, USA") %>%
   brief_entries(what = award,
                 when = time, 
                 with = place)
```

Presentations
============================

```{r presentations}
readr::read_csv(here("./data/presentations.csv")) %>% 
  subset(type == "Oral") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title,
                   where = location)
```

Poster presentations
============================

```{r}
readr::read_csv(here("./data/presentations.csv")) %>% 
  subset(type == "Poster") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title, where = location)
```

Publications
============================

```{r}
library(dplyr)

bibliography_entries(here("./data/references.bib")) %>%
  arrange(desc(issued))
```

Computational skills
============================

- **General**: GWAS analysis, Exome/Genome variant calling, Plink, bedtools
- **R**: Rshiny application development, Rmarkdown, Package development, OMICS data analysis (RNA-seq, single-cell OMICS), reticulate
- **Python**: Jupyter notebooks, basic computer vision applications, single-cell OMICS analysis
- **Containers**: Docker container creation, Singularity usage, Nextflow
- **Galaxy project**: Creation of galaxy tools and wrappers

Languages
============================

- German (mother-language)
- English (fluent)
- French (fluent)