---
headcolor: 00785c
name: Florian
surname: W&uuml;nnemann
position: "Postdoctoral researcher"
address: "Im Neuenheimer Feld 130, 69120 Heidelberg, Germany"
phone: +49 15773482357
www: florianwuennemann.com
email: "florian.wuennemann@gmail.com"
twitter: flowuenne
github: flowuenne
linkedin: florian-w&uuml;nnemann-322357189
# date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Bioinformatics researcher with 5 years of postdoctoral experience in biomedical research at the intersection of data production, processing and analysis for omics technologies."
docname: Curriculum Vitae
output: 
  vitae::awesomecv:
    keep_tex: false
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = FALSE)
library(vitae)
library(tibble)
library(glue)
library(fontawesome)
library(here)
```

\faIcon{chart-bar} Research experience
============================

```{r, research_experience}
readr::read_csv(here("./data/experience.csv")) %>% 
  as_tibble() %>%
  detailed_entries(what = position, 
                   when = glue::glue("{start} - {end}"),
                   with = institution,
                   where = where,
                   why = description)
```


\faIcon{university} Education
============================

```{r, education}
library(tibble)
readr::read_csv(here("./data/education.csv")) %>%
  vitae::detailed_entries(what = degree,
                   when = glue("{start} - {end}"),
                   with = institution,
                   where = where,
                   why = details)
```

\faIcon{laptop-code} Computational skills
============================

- **General**: GWAS analysis, Exome/Genome variant calling, Plink, image analysis (Fiji, Napari, QuPath), basic bash scripting, creation of Galaxy tools and wrappers, setup of https://spatialomics.usegalaxy.eu/
- **Containerization & High-Performance Computing (HPC)**: Docker, Singularity, Nextflow pipeline creation and execution, SLURM, PBS, Virtual machine (VM) management
- **R**: Rshiny application development, Rmarkdown, OMICS data analysis (RNA-seq, single-cell OMICS, spatial OMICS)
- **Python**: Basic computer vision applications, single-cell & spatial OMICS analysis, bioconda, biocontainers

\newpage

\faIcon{laptop} Hackathons
============================

```{r, hackathons}
readr::read_csv(here("./data/hackathons.csv")) %>% 
   detailed_entries(with = title,
                    what = project,
                    when = glue::glue("{start} - {end}"),
                    where = location)
```

\faIcon{dollar-sign} Funding History
============================

```{r, funding}
readr::read_csv(here("./data/scholarships.csv")) %>% 
   detailed_entries(what = scholarship, 
                 when = glue::glue("{start} - {end}"))
```


\faIcon{award} Honors and Awards
============================

```{r, awards}
tribble(~time, ~award, ~place,
        "2021/06","Poster prize: Prix Fonds de recherche du Québec (FRQS) (Recherche fondamentale doctorale / Postdoc)","Montreal,Canada",
        "2019/06","Best oral presentation award, 22nd Montreal Heart Institute research day","Montreal,Canada",
        "2017/05","Best oral presentation award, 32nd student congress at the CHU Sainte-Justine","Montreal, Canada",
        "2016/05","Markwald award for best oral presentation, Weinstein Cardiovascular Development and Regeneration Conference 2016","Durham, USA") %>%
   brief_entries(what = award,
                 when = time, 
                 with = place)
```

\faIcon{scroll} Publications
============================

For a full list of all my scientific publications, please see my Google scholar profile:

[https://scholar.google.de/citations?user=WsGy_hkAAAAJ&hl=de](https://scholar.google.de/citations?user=WsGy_hkAAAAJ&hl=de)

\faIcon{paper-plane} Invited Presentations
============================

```{r invited_presentations}
readr::read_csv(here("./data/presentations.csv")) %>% 
  subset(type == "Invited") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title,
                   where = location)
```

\faIcon{file-powerpoint} Presentations
============================

```{r presentations}
readr::read_csv(here("./data/presentations.csv")) %>% 
  subset(type == "Oral") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title,
                   where = location)
```

\faIcon{chalkboard-teacher} Poster presentations
============================

```{r}
readr::read_csv(here("./data/presentations.csv")) %>% 
  subset(type == "Poster") %>%
  detailed_entries(with = conference, 
                   when = glue::glue("{start} - {end}"), 
                   what = title, where = location)
```

<!-- \faIcon{scroll} Preprints -->
<!-- ============================ -->

<!-- ```{r} -->
<!-- library(dplyr) -->

<!-- bibliography_entries(here("./data/preprint_references.bib")) %>% -->
<!--   arrange(desc(issued)) -->
<!-- ``` -->

<!-- \faIcon{scroll} Publications -->
<!-- ============================ -->

<!-- ```{r} -->
<!-- library(dplyr) -->

<!-- bibliography_entries(here("./test.bib")) %>% -->
<!--   arrange(desc(issued)) -->
<!-- ``` -->

\faIcon{language} Languages
============================
- German (mother-language)
- English (fluent)
- French (fluent)